How to improve PCA based methods of genome scan using ecological data: detecting selection using RDA.

### 2017-02-07 article_genome_scan.tex
update

\title[Constrained ordination for environmental genomics]{Constrained ordination method as a tool for performing genome scan and environmental genomic studies}

>>>>

\title[RDA for environmental genomics]{How to improve PCA based methods of genome scan using ecological data: detecting selection using RDA.}
